An Introduction to Rocker: Docker Containers for R

### 2016-11-20 manuscript.Rmd
outline notes

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Santa Cruz
    address:
    - line 1
    - line 2
    email:  cboettig@ropensci.org
  - name: Dirk Eddlebuettel
    affiliation: Debian, ...
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

@@

@@

@@

@@

## The rstudio image

>>>>

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - line 1
    - line 2
    email:  cboettig@ropensci.org
  - name: Dirk Eddlebuettel
    affiliation: Debian, ...
    address:
    - line 1
    - line 2
    email:  author2@work
abstract: >
  An abstract of less than 150 words.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

@@

- Community-optimized images

- Portability & cloud computing

- Reproducibility

- Convenience

  - Installation of certain packages can be challenging and non-intuitive, particularly when those packages require specific external dependencies. 
  - Many users are reluctant to upgrade their suite of installed packages.  Using the Rocker images, users can try out packages and run code without having to upgrade or otherwise alter their own system's R configuration, which may break existing work

- Instruction

@@

\citep{Boettiger2015}

@@

UBSAN, Clang

@@

## rocker-versioned stack
